---
title: "Compare Model Fits"
author: "Alex"
date: '2022-05-23'
output: html_document
---

```{r setup, include=FALSE}
setwd("..")
# Set Up R Session --------------------------------------------------------

library(MFPCA)
library(tidyverse)
library(patchwork)
library(Matrix)
library(mvtnorm)
library(survival)
library(bamlss)


# Data Generation
source("R/simMultiJM.R")
source("R/preprocessing.R")

# Helperfunction PCRE
source("R/eval_mfun.R")
source("R/pcre_smooth.R")

connection <- paste0("/run/user/1000/gvfs/smb-share:server=clapton.wiwi.hu-ber",
                     "lin.de,share=volkmana.hub/JMbamlss/rirs/")
load(paste0(connection, "mod4.Rdata"))
load(paste0(connection, "mod7.Rdata"))
load(paste0(connection, "mod8.Rdata"))
load(paste0(connection, "mod9.Rdata"))
load(paste0(connection, "mod10.Rdata"))

```

## Compare different Model Fits

```{r, echo = FALSE}
# Generate data with independent random intercepts
d_25 <- simMultiJM(nsub = 150, times = seq(0, 25, by = 0.25), 
                   probmiss = 0.75, maxfac = 1.5,
                   nmark = 2, param_assoc = TRUE, M = NULL, 
                   FPC_bases = NULL, FPC_evals = NULL, mfpc_args = NULL,
                   re_cov_mat = matrix(c(0.68, 0, 0, 0,
                                         0, 0.28, 0, 0,
                                         0, 0, 0.68, 0,
                                         0, 0, 0, 0.28), ncol = 4), 
                   ncovar = 2,
                   lambda = function(t, x) {
                     1.37 * t^(0.37)
                   },
                   gamma = function(x) {
                     - 5.8 + 0.48*x[, 3]
                   },
                   alpha = list(function(t, x) {
                     0.64 + 0*t
                   }, function(t, x) {
                     -0.64 + 0*t
                   }),
                   mu = list(function(t, x, r){
                     2.13 + 0.24*t - 0.25*x[, 3] - 0.05*t*x[, 3] + 
                       r[, 1] + r[, 2]*t
                   }, function(t, x, r){
                     2.13 + 0.24*t - 0.25*x[, 3] - 0.05*t*x[, 3] + 
                       r[, 3] + r[, 4]*t
                   }),
                   sigma = function(t, x) {
                     log(0.6) + 0*t
                   }, 
                   tmax = NULL, seed = 1808, 
                   full = TRUE, file = NULL)
d_1_obs <- d_25$data %>%
  mutate(survtime = survtime / 25, obstime = obstime / 25)
d_1_short <- d_25$data_short %>%
  mutate(survtime = survtime / 25)
d_1_full <- d_25$data_full %>%  
  mutate(survtime = survtime / 25, obstime = obstime / 25)


# MFPC Calculations -------------------------------------------------------

# Use true structure
seq1 <- seq(0, 1, by = 0.01)
set.seed(1808)
n <- 100000
b <- mvtnorm::rmvnorm(n = n, mean = c(0,0,0,0), 
                      sigma = diag(c(0.68, 0.28, 0.68, 0.28)))
mfun1 <- multiFunData(
  funData(argvals = seq1,
          X = (b[, 1:2] %*% matrix(c(rep(1, length(seq1)), seq1),
                                   byrow = TRUE, ncol = length(seq1)))),
  funData(argvals = seq1,
          X = (b[, 3:4] %*% matrix(c(rep(1, length(seq1)), seq1),
                                   byrow = TRUE, ncol = length(seq1))))
)
mfpca_tru <- MFPCA(mFData = mfun1, M = 4,
                   uniExpansions = list(list(type = "uFPCA", npc = 2),
                                        list(type = "uFPCA", npc = 2)))

# Estimate using data
mfpca_es <- preproc_MFPCA(d_1_obs, uni_mean = "y ~ 1+obstime + x3 + obstime:x3",
                          M = 4, npc = 2)


# New data for prediction -------------------------------------------------

ndat_tru <- attach_wfpc(mfpca_tru, d_1_full, eval_weight = FALSE)
ndat_es <- attach_wfpc(mfpca_es, d_1_full, eval_weight = FALSE)

ndat_tru$fit <- predict(b_pc4_s4_1, ndat_tru, model = "mu")
ndat_tru$fit_RE <- predict(b_pc4_s4_1_RE, ndat_tru, model = "mu")
ndat_es$fit <- predict(b_pc4_s4_1_es, ndat_es, model = "mu")
d_1_full$fit_re1 <- predict(b_rirs_1_1, d_1_full, model = "mu")
d_1_full$fit_re2 <- predict(b_rirs_1, d_1_full, model = "mu")



set.seed(1808)
ids <- d_1_short %>%
  mutate(stime = cut(survtime, c(0, 0.3, 0.6, 1))) %>%
  group_by(stime) %>%
  sample_n(5) %>% 
  ungroup() %>% 
  select(id)
id1 <- as.numeric(as.vector(ids[1:5, 1, drop = TRUE]))
id2 <- as.numeric(as.vector(ids[6:10, 1, drop = TRUE]))
id3 <- as.numeric(as.vector(ids[11:15, 1, drop = TRUE]))



```

The simulated and estimated functional principal component functions are the following functions.

```{r, echo=FALSE}
plot(mfpca_tru$functions)
plot(mfpca_es$functions)
```

Plots for three different models (using the simulated FPC basis, using the estimated FPC basis, using RI+RS) for random observations with \$0.6 \<\$ survival \$ \leq 1\$ (the fit is the solid line, the dashed line is the underlying trajectory):

```{r pressure, echo=FALSE, fig.width=12,fig.height=7}
ggplot(data = ndat_tru %>% filter(id %in% id3), 
               aes(x = obstime, colour = id)) +
  theme_bw(base_size = 15) +
  geom_line(aes(y = fit)) +
  geom_line(aes(y = mu), linetype = "dashed") +
  geom_point(data = d_1_obs %>% filter(id %in% id3), 
             aes(y = y, shape = id), size = 2) +
  theme(legend.position = "none") +
  scale_y_continuous("Marker") +
  scale_x_continuous("Time") +
  facet_wrap(~marker, scales = "free") +
  ggtitle("True FPCs")
ggplot(data = ndat_es %>% filter(id %in% id3), 
               aes(x = obstime, colour = id)) +
  theme_bw(base_size = 15) +
  geom_line(aes(y = fit)) +
  geom_line(aes(y = mu), linetype = "dashed") +
  geom_point(data = d_1_obs %>% filter(id %in% id3), 
             aes(y = y, shape = id), size = 2) +
  theme(legend.position = "none") +
  scale_y_continuous("Marker") +
  scale_x_continuous("Time") +
  facet_wrap(~marker, scales = "free") +
  ggtitle("Est FPCs")
ggplot(data = d_1_full %>% filter(id %in% id3), 
                  aes(x = obstime, colour = id)) +
  theme_bw(base_size = 15) +
  geom_line(aes(y = fit_re1)) +
  geom_line(aes(y = mu), linetype = "dashed") +
  geom_point(data = d_1_obs %>% filter(id %in% id3), 
             aes(y = y, shape = id), size = 2) +
  theme(legend.position = "none") +
  scale_y_continuous("Marker") +
  scale_x_continuous("Time") +
  facet_wrap(~marker, scales = "free") +
  ggtitle("RIRS (1 Term)")
ggplot(data = d_1_full %>% filter(id %in% id3), 
                  aes(x = obstime, colour = id)) +
  theme_bw(base_size = 15) +
  geom_line(aes(y = fit_re2)) +
  geom_line(aes(y = mu), linetype = "dashed") +
  geom_point(data = d_1_obs %>% filter(id %in% id3), 
             aes(y = y, shape = id), size = 2) +
  theme(legend.position = "none") +
  scale_y_continuous("Marker") +
  scale_x_continuous("Time") +
  facet_wrap(~marker, scales = "free") +
  ggtitle("RIRS (2 Term)")

```

For random observations with \$ 0.3 \< \$ survival \$ \leq 0.6\$

```{r, echo=FALSE, fig.width=12,fig.height=7}
ggplot(data = ndat_tru %>% filter(id %in% id2), 
               aes(x = obstime, colour = id)) +
  theme_bw(base_size = 15) +
  geom_line(aes(y = fit)) +
  geom_line(aes(y = mu), linetype = "dashed") +
  geom_point(data = d_1_obs %>% filter(id %in% id2), 
             aes(y = y, shape = id), size = 2) +
  theme(legend.position = "none") +
  scale_y_continuous("Marker") +
  scale_x_continuous("Time") +
  facet_wrap(~marker, scales = "free") +
  ggtitle("True FPCs")
ggplot(data = ndat_es %>% filter(id %in% id2), 
               aes(x = obstime, colour = id)) +
  theme_bw(base_size = 15) +
  geom_line(aes(y = fit)) +
  geom_line(aes(y = mu), linetype = "dashed") +
  geom_point(data = d_1_obs %>% filter(id %in% id2), 
             aes(y = y, shape = id), size = 2) +
  theme(legend.position = "none") +
  scale_y_continuous("Marker") +
  scale_x_continuous("Time") +
  facet_wrap(~marker, scales = "free") +
  ggtitle("Est FPCs")
 ggplot(data = d_1_full %>% filter(id %in% id2), 
                  aes(x = obstime, colour = id)) +
  theme_bw(base_size = 15) +
  geom_line(aes(y = fit_re1)) +
  geom_line(aes(y = mu), linetype = "dashed") +
  geom_point(data = d_1_obs %>% filter(id %in% id2), 
             aes(y = y, shape = id), size = 2) +
  theme(legend.position = "none") +
  scale_y_continuous("Marker") +
  scale_x_continuous("Time") +
  facet_wrap(~marker, scales = "free") +
  ggtitle("True RIRS (1 Term)")
ggplot(data = d_1_full %>% filter(id %in% id2), 
                  aes(x = obstime, colour = id)) +
  theme_bw(base_size = 15) +
  geom_line(aes(y = fit_re2)) +
  geom_line(aes(y = mu), linetype = "dashed") +
  geom_point(data = d_1_obs %>% filter(id %in% id2), 
             aes(y = y, shape = id), size = 2) +
  theme(legend.position = "none") +
  scale_y_continuous("Marker") +
  scale_x_continuous("Time") +
  facet_wrap(~marker, scales = "free") +
  ggtitle("RIRS (2 Term)")
```

For random observations with \$ 0\<\$ survival \$ \leq 0.3\$

```{r, echo=FALSE, fig.width=12,fig.height=7}
ggplot(data = ndat_tru %>% filter(id %in% id1), 
               aes(x = obstime, colour = id)) +
  theme_bw(base_size = 15) +
  geom_line(aes(y = fit)) +
  geom_line(aes(y = mu), linetype = "dashed") +
  geom_point(data = d_1_obs %>% filter(id %in% id1), 
             aes(y = y, shape = id), size = 2) +
  theme(legend.position = "none") +
  scale_y_continuous("Marker") +
  scale_x_continuous("Time") +
  facet_wrap(~marker, scales = "free") +
  ggtitle("True FPCs")
ggplot(data = ndat_es %>% filter(id %in% id1), 
               aes(x = obstime, colour = id)) +
  theme_bw(base_size = 15) +
  geom_line(aes(y = fit)) +
  geom_line(aes(y = mu), linetype = "dashed") +
  geom_point(data = d_1_obs %>% filter(id %in% id1), 
             aes(y = y, shape = id), size = 2) +
  theme(legend.position = "none") +
  scale_y_continuous("Marker") +
  scale_x_continuous("Time") +
  facet_wrap(~marker, scales = "free") +
  ggtitle("Est FPCs")
ggplot(data = d_1_full %>% filter(id %in% id1), 
                  aes(x = obstime, colour = id)) +
  theme_bw(base_size = 15) +
  geom_line(aes(y = fit_re1)) +
  geom_line(aes(y = mu), linetype = "dashed") +
  geom_point(data = d_1_obs %>% filter(id %in% id1), 
             aes(y = y, shape = id), size = 2) +
  theme(legend.position = "none") +
  scale_y_continuous("Marker") +
  scale_x_continuous("Time") +
  facet_wrap(~marker, scales = "free") +
  ggtitle("RIRS (1 Term)")
ggplot(data = d_1_full %>% filter(id %in% id1), 
                  aes(x = obstime, colour = id)) +
  theme_bw(base_size = 15) +
  geom_line(aes(y = fit_re2)) +
  geom_line(aes(y = mu), linetype = "dashed") +
  geom_point(data = d_1_obs %>% filter(id %in% id1), 
             aes(y = y, shape = id), size = 2) +
  theme(legend.position = "none") +
  scale_y_continuous("Marker") +
  scale_x_continuous("Time") +
  facet_wrap(~marker, scales = "free") +
  ggtitle("RIRS (2 Term)")
```
