---
title: "Simple MJMs"
author: "Alex"
date: "4/13/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MFPCA)
library(tidyverse)
library(Matrix)
library(mvtnorm)
library(survival)
library(bamlss)


# Data Generation
source("R/simMultiJM.R")
source("R/preprocessing.R")

# Helperfunction PCRE
source("R/eval_mfun.R")
source("R/pcre_smooth.R")

# Family Construction
source("R/mjm_bamlss.R")
source("R/MJM_transform.R")
source("R/opt_MJM.R")
source("R/opt_updating.R")
source("R/MJM_mcmc.R")
source("R/mcmc_proposing.R")
source("R/survint.R")

```

## Idea

Start with simple simulation scenarios for a proof of concept. In particular, start with a multivariate joint model, where the intra-subject association of the longitudinal part is induced only by a random intercept. Then expand it further to more complex scenarios.

The proof of concept follows the outline:
* Data generation
* Data preparation
* Model formula
* Model fit
* Sampling statistics

## Random Intercept Model

```{r, eval = FALSE}
# Generate data with independent random intercepts
d_indepri <- simMultiJM(nsub = 150, times = seq(0, 25, by = 0.25), 
                        probmiss = 0.75, maxfac = 1.5,
                        nmark = 2, param_assoc = TRUE, M = NULL, 
                        FPC_bases = NULL, FPC_evals = NULL, mfpc_args = NULL,
                        re_cov_mat = matrix(c(0.68, 0, 0, 0.68), ncol = 2), 
                        ncovar = 2,
                        lambda = function(t, x) {
                          1.37 * t^(0.37)
                        },
                        gamma = function(x) {
                          - 5.8 + 0.48*x[, 3]
                        },
                        alpha = list(function(t, x) {
                          0.64 + 0*t
                        }, function(t, x) {
                          -0.64 + 0*t
                        }),
                        mu = list(function(t, x, r){
                          2.13 + 0.24*t - 0.25*x[, 3] - 0.05*t*x[, 3] + 
                            r[, 1]
                        }, function(t, x, r){
                          2.13 + 0.24*t - 0.25*x[, 3] - 0.05*t*x[, 3] + 
                            r[, 2]
                        }),
                        sigma = function(t, x) {
                          log(0.6) + 0*t
                        }, 
                        tmax = NULL, seed = 1808, 
                        full = TRUE, file = NULL)

```

